Sparse Function-space Representation \\ of Neural Networks

### 2023-05-13 paper/main.tex

\section{Introduction}
\label{sec:intro}
%
Deep learning has become the cornerstone of contemporary artificial intelligence, proving remarkably effective in tackling supervised and unsupervised learning tasks in the {\em large data}, {\em offline}, and {\em gradient-based training} regime. Despite its success, gradient-based learning techniques exhibit limitations when applied to sequential learning paradigms, such as Continual Learning (CL, \cite{add}) and Reinforcement Learning (RL, \cite{add}). In CL, the challenge is retaining a compact representation of the problem and avoid forgetting over the life-long learning horizon (see, \eg, \cite{add}). Similarly in RL, the model would need to adapt to observations of the environment through exploration, but this can be inefficient and would require constant retraining (\eg, \cite{add, add}).

>>>>

\section{Introduction}
\label{sec:intro}
%
Deep learning has become the cornerstone of contemporary artificial intelligence, proving remarkably effective in tackling supervised and unsupervised learning tasks in the {\em large data}, {\em offline}, and {\em gradient-based training} regime. Despite its success, gradient-based learning techniques exhibit limitations when applied to sequential learning paradigms, such as Continual Learning (CL, \cite{add}) and Reinforcement Learning (RL, \cite{sutton2018reinforcement}). In CL, the challenge is retaining a compact representation of the problem and avoid forgetting over the life-long learning horizon (see, \eg, \cite{add}). Similarly in RL, the model would need to adapt to observations of the environment through exploration, but this can be inefficient and would require constant retraining (\eg, \cite{add, add}).
